Supplement to Effect of COVID-19 burden on changes in HPV vaccination coverage among females between 2019 and 2022

### 2025-04-04 products/manuscript/supplement/Supplementary-Material.qmd
Part 4 Commit 2 - Updating supplementary material and Read Me files

---
title: "Supplement to Effect of COVID-19 burden on changes in HPV vaccination coverage among females between 2019 and 2022"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
---

@@

# Supplemental Information

## Table of contents

-   Code and file information
-   Country characteristic details

# Code and file information

Explain here what each code/file is and does, and in which order (if any) users need to run thing to reproduce everything.
Essentially, give a full set of instructions to re-generate everything.

>>>>

---
title: "Supplement to Effect of COVID-19 burden on changes in HPV vaccination coverage among females between 2019 and 2022"
format:
  docx:
    toc: false
    number-sections: false
    highlight-style: github
---

@@

# Table of contents

-   Project structure and content
-   Country characteristic details
-   Additional analyses

# Project structure and content

This project follows the following folder structure. See the `readme` files in each folder for more details.

* The `assets` folder is a place holder for any files that do not belong in the data, code, results, or products folders. These items are not generated by code.

* The `code` folder contains all coding files required for the project. This folder includes 3 sub-folders that do different parts of an analysis: 
  exploratory data analysis (EDA), processing, and analysis. See the readme files in those folders for details.

* The `data` folder contains all data files required for the project. There are 2 sub-folders, raw-data contains raw data files
  downloaded from their online sourcesand processed-data which contains the cleaned and edited data sets, including a final
  merged project dataset (project_data.rds). All files are saved as .rds files.

* The `products` folder contains a subfolder for the manuscript, 
  - The  `manuscript` subfolder contains a sub-folder for a supplementary material file.

* The `results` folder contains automatically/code generated output. This includes subfolders for figures and tables. 
  All figures are saved as .png files. Most tables are saved as .png and .rds files. Rds files can be used to reference specific 
  values, while the png files will be displayed in the body of the manuscript since Quarto is currently unable to knit tables to 
  Word. All content in these folders are automatically generated by code.

* There are multiple special files in the repo.
  * `readme.md`: this file contains instructions or details about the folder it
  is located in. You are reading the project-level `README.md` file right now. There is a `readme` in almost every folder.
  * `data-analysis-template.Rproj` is a file that tells RStudio that this is the main folder for a project. 
  * a few "hidden" files and folders (they start with a `.` and depending on how your OS is configured, you might not see them). Those are for R/RStudio and Git/GitHub and you can ignore them.

## Steps for reproducing the project

To fully reproduce all steps of the project, the code should be run in the following order:

1. processing-code/processing-code.qmd
2. eda-code/eda_for_manuscript.qmd
3. analysis-code/statistical-analysis.R
4. products/manuscript/Manuscript.qmd
5. products/manuscript/supplement/Supplementary-Material.qmd

Note: Because all data, figures, and tables are saved in the relevant subfolders, the manuscript 
can be produced by simply running the Manuscript.qmd file.
